Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-22 paper/paper.tex
Minor changes

During our work, several interesting lessons were learned about running 
workflow ensembles on cloud infrastructures. One result is that the simple 
strategy used by DPDS performs relatively well in terms of the number of 
workflows completed and the high resource utilization it can achieve. However,
the extra workflows may be of lower-priority, and the high utilization
may be achieved by running tasks from workflows that cannot be completed
given the constraints. On the other hand, DPDS may be the only choice when 
estimates of task runtimes are not available in advance. We also observed
that the WA-DPDS and SPSS algorithms are able to find better quality 
solutions in terms of the target metrics: this is primarily a result of the 
admission algorithms rejecting workflows that are too large to be completed 
given the constraints, and accepting more smaller workflows that can be 
completed.

Another lesson learned from our studies is the effect of task granularity on 
workflow ensembles. All the benchmark workflows that we tested have an average 
number of tasks (50--1000), but the Montage and CyberShake workflows have 
fine-grained tasks with execution times on the order of seconds to minutes, 
while LIGO, Epigenomics and SIPHT have coarser-grained tasks with runtimes 
ranging from several minutes to hours. We observed that the dynamic 
algorithms achieved better results on the fine grained workflows since the 
simple random scheduling strategy leads to good load-balancing and high 
resource utilization for these ensembles. On the other hand, when tasks are
longer, it becomes more beneficial to apply the more sophisticated static 
scheduling strategy of SPSS.

>>>>

During our work, several interesting lessons were learned about running 
workflow ensembles on cloud infrastructures. One result is that the simple 
strategy used by DPDS performs relatively well in terms of the number of 
workflows completed and the high resource utilization it can achieve. However,
some of these workflows may be of lower priority, and the high utilization
may be achieved by running tasks from workflows that cannot be completed
given the constraints. On the other hand, DPDS may be the only choice when 
estimates of task runtimes are not available in advance. We also observed
that the WA-DPDS and SPSS algorithms are able to find better quality 
solutions in terms of the target metrics: this is primarily a result of the 
admission algorithms, which reject workflows that are too large to be 
completed given the constraints, and accept more smaller workflows that 
can be completed.

Another lesson learned from our studies is the effect of task granularity on 
workflow ensembles. All the benchmark workflows that we tested have an average 
number of tasks (50--1000), but the Montage and CyberShake workflows have 
fine-grained tasks with execution times on the order of seconds to minutes, 
while LIGO, Epigenomics and SIPHT have coarser-grained tasks with runtimes 
ranging from several minutes to hours. We observed that the dynamic 
algorithms achieved better results on the fine grained workflows since the 
simple random scheduling strategy leads to good load-balancing and high 
resource utilization for these ensembles. On the other hand, when tasks are
longer, the dynamic algorithms tend to use up the budget by running tasks 
from low-priority workflows while the more sophisticated static scheduling 
strategy of SPSS is more circumspect. In the future we plan to investigate 
the effects of task granularity on ensemble scheduling in a more systematic
fashion.
